Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-29 paper/paper.tex
fix
Draft Artifact section

\subsubsection{Resampling}

@@

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$. The
    average is obtained by resampling the original trace 100 times. The dashed
    lines represent the 10th and 90th percentiles of the values across this
  resampling. Each figure is a different trace, and this figure is followed-up
in figure~\ref{fig:follow} for the UniLu-Gaia log.}

@@

Authors are sorted in alphabetical order. We gracefully thank the contributors
of the Parallel Workloads Archive, Victor Hazlewood (SDSC SP2), Travis Earheart
and Nancy Wilkins-Diehr (SDSC Blue), Lars Malinowsky (KTH SP2), Dan Dwyer and
Steve Hotovy (CTC SP2), Joseph Emeras (CEA Curie and UniLu Gaia), Susan
Coghlan, Narayan Desay, Wei Tang (ANL Intrepid), and of course Dror Feitelson.
The Metacentrum workload log was graciously provided by the Czech National Grid
Infrastructure MetaCentrum. This work has been partially supported by the LabEx
PERSYVAL-Lab(\grantsponsor{ANR-11-LABX-0025-01}{ANR-11-LABX-0025-01}) funded by
the French program Investissement d'avenir. Experiments presented in this paper
were carried out using the Grid'5000 testbed. Grid'5000 is supported by a
scientific interest group hosted by Inria and including CNRS, RENATER and
several Universities as well as other
organizations\footnote{https://www.grid5000.fr}.  Access to the experimental
machine(s) used in this paper was gracefully granted by research teams from
LIG\footnote{http://www.liglab.fr} and Inria\footnote{http://www.inria.fr}.

@@

We develop a lightweight simulator~\cite{ocst} and an accompanying multi-armed
bandit library~\cite{obandit}. Both are made available under the ISC~\cite{isc}
license and released as persistent Zenodo~\cite{zenodo} archives. Additionally,
we provide a workflow written in the zymake~\cite{breck2008zymake} format that
is able to generate all the figures from this paper and its annexes. All these
parts and their dependencies are packaged via Nix~\cite{nix} expressions.
to use the
archive at~\cite{repro} on any linux system equipped with the Nix package manager.
Generating the figures is done with:

\begin{lstlisting}
wget ".." -o banditeasy.tgz
tar -vzf banditeasy.tgz
cd banditeasy
nix-build
\end{lstlisting}

\end{document}

>>>>

\subsubsection{Resampling}
\label{ssub:resampling}

@@

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$. The
    average is obtained by resampling the original trace 100 times. The dashed
    lines represent the 10th and 90th percentiles of the values across this
  resampling.}

@@

Authors are sorted in alphabetical order. We warmly thank Pierre Neyron for help with the experiments. We gracefully thank the contributors
of the Parallel Workloads Archive, Victor Hazlewood (SDSC SP2), Travis Earheart
and Nancy Wilkins-Diehr (SDSC Blue), Lars Malinowsky (KTH SP2), Dan Dwyer and
Steve Hotovy (CTC SP2), Joseph Emeras (CEA Curie and UniLu Gaia), Susan
Coghlan, Narayan Desay, Wei Tang (ANL Intrepid), and of course Dror Feitelson.
The Metacentrum workload log was graciously provided by the Czech National Grid
Infrastructure MetaCentrum. This work has been partially supported by the LabEx
PERSYVAL-Lab(\grantsponsor{ANR-11-LABX-0025-01}{ANR-11-LABX-0025-01}) funded by
the French program Investissement d'avenir. Experiments presented in this paper
were carried out using the Grid'5000 testbed. Grid'5000 is supported by a
scientific interest group hosted by Inria and including CNRS, RENATER and
several Universities as well as other
organizations\footnote{https://www.grid5000.fr}.  Access to the experimental
machine(s) used in this paper was gracefully granted by research teams from
LIG\footnote{http://www.liglab.fr} and Inria\footnote{http://www.inria.fr}.

@@

In this annex, we describe the computational artifacts associated with this
work. We take a lightweight approach to replicability by packaging a workflow
that generates all the figures from this paper and making it available
publicly. Moreover, questions regarding replication can be freely directed at
the authors via e-mail.

All the code associated with this work is released under the ~\cite{ISC}
license as a persistent Zenodo~\cite{zenodo} archive at~\cite{zenodomain}.

\subsection{Packaging and Replicability}

There are various approaches for making computational experiments replicable,
among which distributing complete operating system images, containers, or
packaging software. As our experiments are CPU bound, we decide to opt for the
software packaging approach using the Nix~\cite{nix} packaging system.  All the
dependencies of our experiments (including our own code, dependencies for data
processing and visualization and workflow engine) are automatically managed by
Nix up to the actual execution of the code.

Running the experiments can be done on any platform equipped with the nix
workflow system by running:

\begin{lstlisting}
nix-build (fetchTarball ...) -A banditSelection
\end{lstlisting}

\subsection{Testbed}

 The experiments in this paper can run via in less than 24 hours on a large
 machine. More precisely, we had access to a Dell PowerEdge R730 equipped with
 a total of 56 threads @2.4GHz each and 757G of RAM.  For this reason, the
 experimental campaign was designed to be executed on a single host.

 \subsection{Workflow}

 All experiments are tied together using Zymake~\cite{zymake}, a minimalistic
 workflow system designed for computational experiments. This system is
 analogous to a traditional build system with added workflow capabilities. The
 entire workflow that generates this article from the input data is contained
 in a single \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile| to be
 found at the root of the main archive. This workfloww is composed of the
 following steps:

 \begin{itemize}

   \item[Preprocessing]: Data extraction from archives, filtering, resampling.
     This is principally using shell scripts for data manipulation (see file
     \lstinline[basicstyle=\ttfamily\color{blue}]|misc/strong\_filter| for the
     filtering steps used) and ocaml code that implements the resampling method
     described in~\ref{sub:resampling}.

   \item[Simulation]: This step runs the lightweight ocaml backfilling
     simulator specially written for this work. This simulator is made
     available under the ISC~\cite{ISC} license both as a persistent Zenodo
     archive at~\cite{ocst} and as a git repository at ~\cite{ocstgit}.

   \item[Analysis]: This step runs mostly R code that generates the figures
     presented in this paper.
 \end{itemize}
\end{document}
